---
title: "Results"
---

```{r}
#| file: draft-results-code.R
#| include: false
```

## Water Temperature

The analysis shows a seasonal increase in water temperature from April through October. Temperatures peak in the month of July and August with mean temperatures of **86.62°F (95% CI: 86.57-86.68)** and **86.35°F** **(95% CI: 86.31-86.38)**. With the peaks these months were identified with high risk. The months **June (45.5%)** and **September (32%)** are at moderate-risk months. Other months represent low risk **(<20%)**. Based on @fig-temp-time the projected temperatures from June to September roughly around 85°F.

```{r, echo = FALSE}
#| label: fig-temp-time
#| fig-cap: This figure shows the mean temperature throughout each year from 2002 to 2025. The line shows the threshold where a power plant would need to run at reduced risk.
#| message: FALSE

library(ggplot2)
library(dplyr)
library(scales)
library(lubridate)


ggplot(mtempm, aes(Year, Mean_Temp)) + 
  geom_line(aes(
            group = Month)) +
  geom_hline(yintercept = 85, color = "red") +
  theme (axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  facet_wrap(~Month) +
  scale_y_continuous(limits = c(40, 90)) +
  labs(
    title = "Temperature over Years",
    x = "Year",
    y = "Temperature")

```

## Power Requirement

Alabama Power Company produces a com  bined capacity of 14 million Kilowatts (122.72 million megawatt-hours) [@generati]. James M. Barry Power Plant contributes to **10.3%** of the maximum capacity. Total electrical demand represents approximately 40.4% of Alabama Power Company's total  capacity. James M. Barry Power Plant contributes to around **4.2%** of the overall consumption. As shown in @fig-rc-time generation remains sufficient across all reduced capacity scenarios. The highest percentage consumed is April of 2023 at **50%** of capacity, under a **30%** reduced capacity rate. The projected months did not show to have impactful rates.

The analyses shows that the impact of running at reduced capacity is minimal assuming that the plant was running at regular capacity. The highest consumed month was April, which corresponds to a low-risk period of needing to be at reduced capacity.

```{r, echo = FALSE}
#| label: fig-rc-time
#| fig-cap: This figure shows the generation proficiency at different operational capabilities at a given time. Transparency is denoted by percentage consumed. The projected Net generation is denoted by years after the verticle line at the start 2026.

ngen$time <- as.Date(
  paste(ngen$Year, ngen$Month, "01", sep = "-"),
  format = "%Y-%b-%d"
)



ggplot(ngen, aes(x = time, y = net_gen)) +
  geom_line(aes(alpha = pu,
                group = Capacity,
                color = Year > 2025)) +
  scale_y_continuous(labels = label_number(scale = 1e-6, suffix = "M")) +
  facet_wrap(~factor(Capacity)) +
  theme (axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  geom_vline(xintercept = as.Date("2026-01-01")) +
  scale_alpha(range = c(1, 0.1)) +
  scale_color_manual(values = c("FALSE" = "#0072B2", "TRUE" = "#E69F00"),
                     labels = c("Observed", "Projected")) +
  guides(alpha = "none") +
  labs(
    title = "Net Generation Over Time",
    x = "Year",
    y = "Generated Megawatt Hours",
    color = "Status"
  )
```
